\documentclass{article}
\title{2021 - 2022 Plan For JGHS Robotics}
\author{Diego Contreras \\ Robotics Master}
% \date{2017 Jan 23423}

\begin{document}
\maketitle

\newpage
\tableofcontents

\newpage

\begin{abstract}
Robotics is very cool, Kanye
\end{abstract}

\newpage

\section{Introduction - \textit{The place where it all begins}}
This is the first sentence in my introduction. \textit{This sentence is italized.} \textbf{This sentence if bold.} \textsc{This sentence is in small caps.} \texttt{This sentence is in typewritter style.} \emph{This sentence is emphasized}

\textit{This sentence is in italics but the (This issue is not central to our paper.\footnote{We leave it for future work.}) last word is \emph{emphasized}.}

``This quote is correct''
''This quote is incorrect''
"Wtf is this"

This is a sentence\\
This is after a line break

This is a brand new paragraph


\subsection{Sub Introduction}
This is some stuff that' s bit more specific.

\subsubsection{Sub Sub Introduction}
This is some very specific stuff.


\section*{Introduction}
This is the first sentence in my introduction.

\subsection*{Sub Introduction}
This is some stuff that' s bit more specific.

\subsubsection*{Sub Sub Introduction}
This is some very specific stuff.

Here's some other content.

\newpage

\section{\textsc{The Next Page}}
Yes, this is the next page. Don't be intimated. This issue is not central to our paper.\footnote{We leave it for future work.} Here's a list why:

\begin{enumerate}
\item It's easy to be calm
\item It's just a fucking book
\item \textasciicircum
\end{enumerate}

Not enough? Here's some more:

\begin{itemize}
\item It's easy to be calm
\item It's just a fucking book
\item \textasciicircum
\end{itemize}
Blahblahblah

\begin{itemize}
\item something
	\begin{enumerate}
	\item of one type
	\item of another type
	\end{enumerate}
\item something else
	\begin{description}
	\item[car] a four wheeled vehicle.
	\item[bicycle] a two-wheeled vehicle.
	\end{description}
\item something more
\end{itemize}

\newpage
\section{Professional Tables}
\begin{tabular}{lll}
item & type & amount\\
car & vehicle & one\\
bread & food & three
\end{tabular}
\section{Outlined Tables}
\begin{tabular}{|l|l|l|}
item & type & amount\\
car & vehicle & one\\
bread & food & three
\end{tabular}\\
\\\\or\\\\
\begin{tabular}{|lll|}
item & type & amount\\
car & vehicle & one\\
bread & food & three
\end{tabular}
\\\\or\\\\
\begin{tabular}{|l|l|l|}
\hline
item & type & amount\\
\hline
car & vehicle & one\\
\hline
bread & food & three\\
\hline
\end{tabular}\\
\\\\or\\\\\\

\begin{table}
\centering
\begin{tabular}{lll}
\textit{item} & \textit{type} & \textit{amount}\\
\hline
car & vehicle & one\\
bread & food & three\\
\end{tabular}
\caption{Summary of products bought.}
\end{table}



















\end{document}